Age-related changes in plant growth and traits

### 2016-12-13 Analaysis-RA.Rmd
Restructure materials for MS into folders
ignore generated figures
keep current version in single directory

data <- select(SummarySppAge[["mean"]], species, age, repro_inv, growth_leaf, leaf_replacement,leaf_area_0,leaf_weight_0,total_inv,prop_surplus,
  growth_stem, leaf_shed,prop_stem,prop_leaf_replacement,prop_leaf_expand,prop_repro,RA_max_1,lifespan,height, RA_vs_all_leaf,
  LL_death,height_0,total_weight_0,all_leaf_inv)
data$leaf_shed2 <- data$leaf_weight_0 / data$LL_death
data_ind <- select(SummaryInd,species,individual,age, LL_death,height_0,leaf_shed,leaf_weight_0,
                   growth_leaf_pos,repro_inv,total_weight_0,all_leaf_inv,total_inv,surplus_energy)

@@

  plot(NA, log = "xy", xlim = c((min(data_sp_ind$total_weight_0)*0.9),(max(data_sp_ind$total_weight_0)*1.1)), ylim=c(1,(max(data_sp_ind$total_inv)*0.7)),xaxs = "i", yaxs = "i", xaxt="n", ylab="n")
  box()
  axis(1, labels = (i %in% c(7,14)))
  points(x = data_sp_ind$total_weight_0, y = data_sp_ind$all_leaf_inv, col = "darkseagreen4", lwd=2,type="p",pch=1,cex=1.4)
  points(x = data_sp_ind$total_weight_0, y = data_sp_ind$repro_inv, col = "coral3", lwd=2,type="p",pch=1,cex=1.4)
  points(x = data_sp_ind$total_weight_0, y = data_sp_ind$growth_leaf_pos, col = "darkseagreen2", lwd=2,type="p",pch=1,cex=1.4)
  mtext(labels.spp.full(all_species[i]), 3, 0)

@@

```{r}
#FIGURE 2
par(mfrow = c(7,3), cex = 1, oma = c(5, 5, 1, 1), mar = c(0, 3, 2, 1))

@@

  #proportion different energy
  plot(NA, log = "x", ylim = c(0, 1),  xlim = c(1.4, 32), xaxs = "i", yaxs = "i", axes= FALSE, ann=FALSE)
  box()
  axis(1, labels = (i %in% c(7,14)))
  axis(2, at = c(0, 0.2, 0.4, 0.6, 0.8, 1), labels = c(0,"","","","",1), las=1)

  polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_stem, 0, 0), col = "burlywood4", density = NA)
  polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_leaf_replacement, 0, 0), col = "darkseagreen4", density = NA)
  polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_leaf_expand, 0, 0), col = "darkseagreen2", density = NA)
  polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_repro, 0, 0), col = "coral3", density = NA)

  if (i %in% c(4,11)) {
    mtext("Proportional allocation to all energy sinks", 2, line=2, outer=FALSE)
  }
}
```

@@

#panel 1
  plot(NA, log = "xy", xlim = c(1,(max(data_sp_ind$all_leaf_inv)*1.1)),  ylim = c(1,(max(data_sp_ind$repro_inv)*1.1)), xaxs = "i", yaxs = "i", axes= FALSE, ann=FALSE)
  box()
  points(x = data_sp_ind$all_leaf_inv, y = data_sp_ind$repro_inv, col = "darkseagreen4", lwd=2,type="p",pch=1,cex=1.4)

#panel 2
  plot(NA, log = "xy", xlim = c(1,(max(data_sp_ind$growth_leaf_pos)*1.1)),  ylim = c(1,(max(data_sp_ind$repro_inv)*1.1)), xaxs = "i", yaxs = "i", axes= FALSE, ann=FALSE)
  box()
  points(x = data_sp_ind$growth_leaf_pos, y = data_sp_ind$repro_inv, col = "darkseagreen4", lwd=2,type="p",pch=1,cex=1.4)

@@

>>>>

SummarySppAge[["mean"]]$leaf_shed_mean <- SummaryInd %>%
        group_by(species,age) %>%
        summarise(mean(leaf_shed_mean))

SummarySppAge[["mean"]]$leaf_replacement_mean <- SummaryInd %>%
        group_by(species,age) %>%
        summarise(mean(leaf_replacement_mean))

data <- select(SummarySppAge[["mean"]], species, age, repro_inv, growth_leaf, leaf_replacement,leaf_area_0,leaf_weight_0,total_inv,prop_surplus,
  growth_stem, leaf_shed,prop_stem,prop_leaf_replacement,prop_leaf_expand,prop_repro,RA_max_1,lifespan,height, RA_vs_all_leaf,
  LL_death,height_0,total_weight_0,all_leaf_inv,surplus_inv,all_leaf_and_repro_inv,propagule_inv,ovule_count,success_inv)
data$leaf_shed2 <- data$leaf_weight_0 / data$LL_death
data_ind <- select(SummaryInd,species,individual,age, LL_death,height_0,leaf_shed,leaf_weight_0,propagule_inv,ovule_count,
                   growth_leaf_pos,repro_inv,total_weight_0,all_leaf_inv,total_inv,surplus_inv,all_leaf_and_repro_inv,age,success_inv)

@@

  plot(NA, log = "xy", xlim = c((min(data_sp_ind$total_weight_0)*0.9),(max(data_sp_ind$total_weight_0)*1.1)), ylim=c(1,(max(data_sp_ind$total_inv)*0.7)),xaxs = "i", yaxs = "i", xaxt="n", ylab="n")
  box()
  axis(1, labels = (i %in% c(7,14)))
  points(x = data_sp_ind$leaf_weight_0, y = data_sp_ind$all_leaf_inv, col = "darkseagreen4", lwd=2,type="p",pch=1,cex=1.4)
  points(x = data_sp_ind$leaf_weight_0, y = data_sp_ind$repro_inv, col = "coral3", lwd=2,type="p",pch=1,cex=1.4)
  points(x = data_sp_ind$leaf_weight_0, y = data_sp_ind$growth_leaf_pos, col = "darkseagreen2", lwd=2,type="p",pch=1,cex=1.4)
  mtext(labels.spp.full(all_species[i]), 3, 0)

@@

```{r}
#FIGURE 2
par(mfrow = c(7,4), cex = 1, oma = c(5, 5, 1, 1), mar = c(0, 3, 2, 1))

@@

  #proportion different energy
  # plot(NA, log = "x", ylim = c(0, 1),  xlim = c(1.4, 32), xaxs = "i", yaxs = "i", axes= FALSE, ann=FALSE)
  # box()
  # axis(1, labels = (i %in% c(7,14)))
  # axis(2, at = c(0, 0.2, 0.4, 0.6, 0.8, 1), labels = c(0,"","","","",1), las=1)
  # 
  # 
  # polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_stem, 0, 0), col = "burlywood4", density = NA)
  # polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_leaf_replacement, 0, 0), col = "darkseagreen4", density = NA)
  # polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_leaf_expand, 0, 0), col = "darkseagreen2", density = NA)
  # polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_repro, 0, 0), col = "coral3", density = NA)
  # 
  # if (i %in% c(4,11)) {
  #   mtext("Proportional allocation to all energy sinks", 2, line=2, outer=FALSE)
  # }
}
```

@@

#panel 1
 plot(repro_inv ~ leaf_weight_0,data_sp_ind,log="xy",pch=16,xaxt="n")
 points(repro_inv ~ growth_leaf_pos,data_sp_ind,log="xy",pch=16,xaxt="n",col="darkseagreen4")
 points(repro_inv ~ all_leaf_inv,data_sp_ind,log="xy",pch=16,xaxt="n",col="darkseagreen2")
 abline(0,1)
 mtext(labels.spp.full(all_species[i]), 3, 0)

 plot(ovule_count ~ leaf_weight_0,data_sp_ind,log="xy",pch=16,xaxt="n",col=col.age(age))
 #points(leaf_weight_0 ~ ovule_count,data_sp_ind,log="xy",pch=1,xaxt="n",col=col.age(age))
 #points(surplus_inv ~ leaf_weight_0,data_sp_ind,log="xy",pch=14,xaxt="n",col=col.age(age))
 #points(repro_inv ~ growth_leaf_pos,data_sp_ind,log="xy",pch=16,xaxt="n",col="darkseagreen4")
 #points(repro_inv ~ all_leaf_inv,data_sp_ind,log="xy",pch=16,xaxt="n",col="darkseagreen2")
 abline(0,1)
 mtext(labels.spp.full(all_species[i]), 3, 0)

#panel 2
 #  plot(all_leaf_and_repro_inv ~ leaf_weight_0,data_sp_ind,log="xy",pch=16,xaxt="n")
 # points(surplus_inv ~ total_weight_0,data_sp_ind,log="xy",pch=16,xaxt="n",col="darkseagreen2")
 # abline(0,1)
 # mtext(labels.spp.full(all_species[i]), 3, 0)

@@

```{r}
yvar <- "repro_inv"
xvar <- "leaf_weight_0"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope.test=1)
results <- fit$groupsummary
results$r2 <- format(results$r2,digits=2)
results$pval <- format(results$pval,digits=3)
acc_slopes <- dplyr::select(results,group,n,r2,pval)
names(acc_slopes) <- c("species","n_leaf_weight","r2_leaf_weight","p_leaf_weight")

yvar <- "repro_inv"
xvar <- "growth_leaf_pos"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=1)
results <- fit$groupsummary
results$r2 <- format(results$r2,digits=2)
results$pval <- format(results$pval,digits=3)
acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
names(acc_slopes2) <- c("species","n_growth_leaf","r2_growth_leaf","p_growth_leaf")
acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")

yvar <- "repro_inv"
xvar <- "all_leaf_inv"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=1)
results <- fit$groupsummary
results$r2 <- format(results$r2,digits=2)
results$pval <- format(results$pval,digits=3)
acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
names(acc_slopes2) <- c("species","n_all_leaf_inv","r2_all_leaf_inv","p_all_leaf_inv")
acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")

acc_slopes$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")

write.csv(acc_slopes, file="ms/RA/Table_XX_best_predictor_repro_inv.csv",row.names=FALSE)
```

```{r}
yvar <- "surplus_inv"
xvar <- "leaf_weight_0"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope.test=1)
results <- fit$groupsummary
results$r2 <- format(results$r2,digits=2)
results$pval <- format(results$pval,digits=3)
acc_slopes <- dplyr::select(results,group,n,r2,pval)
names(acc_slopes) <- c("species","n_lsurplus","r2_surplus","p_surplus")

yvar <- "all_leaf_and_repro_inv"
xvar <- "leaf_weight_0"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=1)
results <- fit$groupsummary
results$r2 <- format(results$r2,digits=2)
results$pval <- format(results$pval,digits=3)
acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
names(acc_slopes2) <- c("species","n_leaf_and_repro","r2_leaf_and_repro","p_leaf_and_repro")
acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")

yvar <- "all_leaf_inv"
xvar <- "leaf_weight_0"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=1)
results <- fit$groupsummary
results$r2 <- format(results$r2,digits=2)
results$pval <- format(results$pval,digits=3)
acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
names(acc_slopes2) <- c("species","n_all_leaf_inv","r2_all_leaf_inv","p_all_leaf_inv")
acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")

acc_slopes$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")

write.csv(acc_slopes, file="ms/RA/Table_XX_best_predictor_leaf_weight.csv",row.names=FALSE)
```

yvar <- "ovule_count"
xvar <- "leaf_weight_0"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=1)
results <- fit$groupsummary
results

### 2016-12-13 Analysis-accessory.Rmd
Restructure materials for MS into folders
ignore generated figures
keep current version in single directory

plot(seedset~scaled_provisioning_costs,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species),yaxt="n",xaxt="n",ylab="",xlab="",cex=1)

mod_ovule <- sma(choosiness~prop_pollen_attract_vs_success,data=SummarySpp[["mean"]],log="xy",method="SMA")

mod_x <- sma(accessory_inv~embryo_endo_inv,data=SummarySpp[["mean"]],log="xy",method="SMA")
mod_x <- sma(accessory_costs~embryo_endo_costs,data=SummarySpp[["mean"]],log="xy",method="SMA")
plot(zygote_set~embryo_endo_costs,SummaryInd,pch=16,log="x",col=col.spp(species),cex=1)

@@

write.csv(acc_costs_spp_format, file="ms/Accessory/Table01_AccCosts_by_Species.csv",row.names=FALSE)
```

#Table 1. color dots
```{r}
win.metafile("ms/Accessory/Table01_dots.wmf", height=3, width=.2)
plot

@@

plot(y~x,dots,cex=1.5,pch=16,xlab="",ylab="",xaxt="n",yaxt="n",col=col.spp(dots$species),bty="n",xlim=c(0.8,1.2),ylim=c(1.8,28.2))

dev.off()
```
summary(slopes)

@@

write.csv(acc_slopes, file="ms/Accessory/Table02_acc_cost_embryo_size_slopes.csv",row.names=FALSE)
```

#Table Supplementary.correlations between repro inv and propagule inv by species
```{r}
mod_propagule_inv_all <- sma(repro_inv~propagule_inv,data=SummaryInd,log="xy",method="SMA")
mod_propagule_inv_all

mod_flower_inv_all <- sma(repro_inv~flower_inv,data=SummaryInd,log="xy",method="SMA")
mod_flower_inv_all

yvar <- "repro_inv"
xvar <- "propagule_inv"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope.test=mod_propagule_inv_all$groupsummary["Slope"][[1]],elev.test=mod_propagule_inv_all$coef[[1]][1,1])
results <- fit$groupsummary
results$r2 <- format(results$r2,digits=2)
results$pval <- format(results$pval,digits=3)
acc_slopes <- dplyr::select(results,group,n,r2,pval)
names(acc_slopes) <- c("species","n_propagule","r2_propagule","p_propagule")

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=mod_flower_inv_all$groupsummary["Slope"][[1]],elev.test=mod_flower_inv_all$coef[[1]][1,1])
results <- fit$groupsummary
results$r2 <- format(results$r2,digits=2)
results$pval <- format(results$pval,digits=3)
acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
names(acc_slopes2) <- c("species","n_flower","r2_flower","p_flower")
acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")
acc_slopes$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")

write.csv(acc_slopes, file="ms/Accessory/Table_SXX_propagule_invest_vs_all_repropro_inv.csv",row.names=FALSE)
```

@@

write.csv(results, file="ms/Accessory/Table03_correlations_with_repro_inv.csv",row.names=FALSE)
```

#Figure 01. predictions
```{r}
win.metafile("ms/Accessory/Figure01b&c_predictions.wmf", height=3, width=6)
plot

par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05)) 
plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.2,x1=.9,y0=.9,y1=.2,lty=2)
segments(x0=.1,x1=.8,y0=.8,y1=.1,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="count, scaled to plant size",side=2,line=1.1,outer=FALSE,cex=0.8)
mtext(text="costs (mg/seed)",side=1,line=1.0,outer=FALSE,cex=0.8)
legend("bottomleft",legend=c("seed count by reproductive costs","initiated ovules count by pollen-attraction costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
extra.top.left("b",2,1)

@@

win.metafile("ms/Accessory/Figure01def_predictions.wmf", height=6, width=6)
plot

@@

#Figure 2
```{r}
win.metafile("ms/Accessory/Figure02.wmf", height=9, width=6)
plot

@@

#Figure 2 OLD. Scaling of accessory costs versus weight of embryo + endosperm, by species
```{r}
win.metafile("ms/Accessory_Costs/Figure02_embryo_size_acc_cost_correlations.wmf", height=9, width=10)
plot

par(mfrow=c(2,2), cex=1, omi=c(1,.1,.05,.05), mai=c(.2,.8,.1,.05)) 
options(scipen = 5)

plot((ovule_count/seed_count)~prop_pollen_attract_vs_all_repro_all_repro,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species),ylab="",ylim=c(.8,500),yaxt="n",xlim=c(.0015,.5),xaxt="n")
axis(2, at=c(1,10,100), labels=c(1,10,100),cex.axis=1)
axis(1, at=c(0.001,0.005,0.01,0.05,0.1,0.5), labels=c(0.001,0.005,0.01,0.05,0.1,0.5),cex.axis=1)
mtext("choosiness (ovules initiated per seed matured)",2,line=2.3)
mtext("proportion reproductive investment for successful pollen attraction costs",1,line=2.3)

mod_choosy <- sma((ovule_count/seed_count)~prop_pollen_attract_vs_all_repro_all_repro,data=SummarySpp[["mean"]],log="xy",slope=-1,method="SMA")

line_function_log_xy(SummarySpp[["mean"]]$prop_pollen_attract_vs_all_repro_all_repro,mod_choosy,1)
summary(mod_choosy)

plot(seedset~embryo_endo_costs,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.002,500),ylim=c(.004,.6),cex=1.5,xaxt="n",xlab="",ylab="")
mod <- sma(seedset~embryo_endo_costs,SummarySpp[["mean"]],log="xy", method="SMA")
y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
#text((10^(0.99*(par("usr")[2]-par("usr")[1])+par("usr")[1])),(10^(0.97*(par("usr")[4]-par("usr")[3])+par("usr")[3])),paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod,1)
axis(1, at=c(0.01,1,100), labels=c("","",""),cex.axis=1)
mtext("seed set",2,line=2.3)
extra.top.left.logxy("b",2,1.2)
summary(mod)

plot(pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$pollen_attract_costs,SummarySpp[["se"]]$pollen_attract_costs)

points(provisioning_costs~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=21,cex=1.5)
y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$provisioning_costs,SummarySpp[["se"]]$provisioning_costs)

axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=1)
mtext("costs (mg/ovule)",2,line=2.3)

mod_prepollen <- sma(pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],log="xy",method="SMA")
mod_provision <- sma(postpollen_all_per_seed~embryo_endo_costs,SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_prepollen$groupsummary["Slope"][[1]])

line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod_prepollen,1)
line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod_provision,2)

legend("topright",legend=c("pollen attraction","provisioning"),col=c("black","black"),pch=c(16,21),bty="n")
extra.top.left.logxy("c",2,1.2)

plot(prop_pollen_attract_vs_all_repro~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="x", yaxt="n",xaxt="n", ylim=c(0,1), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
points(prop_prepollen_all_vs_all_repro~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=1,cex=1.5)
axis(2, at=c(0,.5,1), labels=c(0,0.5,1.0),cex.axis=1)
axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=1)
extra.top.left.logx("d",2,1.2)

mod_prop_pollen_attract_vs_all_repro <- sma(prop_pollen_attract_vs_all_repro~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="SMA",slope.test=0)
mod_prop_prepollen_all_vs_all_repro <- sma(prop_prepollen_all_vs_all_repro~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="SMA",slope.test=0)

line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_pollen_attract_vs_all_repro,1)

summary(mod_prop_pollen_attract_vs_all_repro)
summary(mod_prop_prepollen_all_vs_all_repro)

plot(prop_postpollen_success~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="x", yaxt="n",xaxt="n", ylim=c(0,1), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
points(prop_prepollen_success~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=1,cex=1.5)
axis(2, at=c(0,.5,1), labels=c(0,0.5,1.0),cex.axis=1)
axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=1)
extra.top.left.logx("d",2,1.2)

mod_prop_postpollen_success <- sma(prop_postpollen_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="SMA")
mod_prop_prepollen_success <- sma(prop_prepollen_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="SMA")

line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_postpollen_success,1)
line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_prepollen_success,3)

summary(mod_prop_postpollen_success)
summary(mod_prop_prepollen_success)

mtext(text="     seed size (mg)",side=1,line=1.5,outer=TRUE,adj=0.5)
mtext(text="                     parental pessimist",line=3,side=1,adj=0,outer=TRUE,font=3)
mtext(text="parental optimist    ",line=3,side=1,adj=1,outer=TRUE,font=3)

#Figure 3. Correlations of various reproductive investment categories against plant weight
```{r}
win.metafile("ms/Accessory/Figure03_correlations_with_plant_weight.wmf", height=5, width=10)
plot

@@

#Supplementary Table. Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
```{r}
win.metafile("ms/Accessory/Figure_SXX_RE_RA_size_age_patterns.wmf", height=10, width=10)
plot

@@

write.csv(results, file="ms/Accessory/Table05a_accessory_vs_all_repro.csv",row.names=FALSE)

@@

write.csv(results, file="ms/Accessory/Table05b_accessory_vs_total_weight.csv",row.names=FALSE)

@@

write.csv(results, file="ms/Accessory/Table05c_accessory_vs_age.csv",row.names=FALSE)
dev.off()
```

@@

write.csv(acc_slopes, file="ms/Accessory/Table_S1_extra_flower_invest_vs_all_repro_inv.csv",row.names=FALSE)
```

@@

write.csv(results, file="ms/Accessory_Costs/Table07_EXTRA_correlations_with_repro_inv.csv",row.names=FALSE)
```

@@

```{r}
Cairo("ms/Accessory_Costs/FigureXX_seedcount_reprocount.svg", height=5, width=5,type="svg",pointsize=10,units="in")
#win.metafile("ms/Accessory_Costs/FigureXX_seedcount_reprocount.wmf", height=5, width=5)

plot

par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,0.05), mai=c(.8,.8,.1,0.1))
options(scipen = 2)

xvar <- "ovule_count"
yvar <- "seed_count"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope=1)
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="buds initiated (count)",ylab="seed count",lty=results$linetype,xlim=c(0.9,20000),ylim=c(0.9,20000))

dplyr::select(results,group,n,r2,pval,Slope,Slope_test_p)
abline(0,1,lwd=2)
abline(-2,1,lwd=2)

legend_with_r2(results,"topleft")

#Although very little energy goes into propagules (or embryos) a notable amount of energy is required for successful seeds to form
```{r}
win.metafile("ms/Accessory_Costs/FigureXX_success_vs_discarded.wmf", height=6, width=8)
plot

@@

#This effect is true across species, since larger-seeded species produce fewer seeds and have higher per seed accessory costs and true within species, since absolute accessory investment is a function of plant size not seedset
```{r}
win.metafile("ms/Accessory_Costs/FigureXX_EXTRA_acc_cost_by_seed_count.wmf", height=5, width=5)
plot

@@

write.csv(results, file="ms/Accessory_Costs/TableXX_seedcount_vs_accessory.csv",row.names=FALSE)

>>>>

```{r}
library(digest)
library(Rcpp)
library(reshape2)
library(tibble)
library(smatr)
library(broom)
library(dplyr)
library(stats)
library(scales)
library(colorspace)

remake::make("export")

SummaryInd <- readRDS("export/SummaryInd.rds")
SummarySpp <- readRDS("export/SummarySpp.rds")
SummarySppAge <- readRDS("export/SummarySppAge.rds")
HarvestData <- readRDS("export/HarvestData.rds")
InvestmentByPart <- readRDS("export/Investment_FD_all.rds")
PartsSummary <- readRDS("export/PartsSummary_all.rds")

source("R/figures.R")
```

@@

write.csv(acc_costs_spp_format, file="ms/Accessory/output/Table01_AccCosts_by_Species.csv",row.names=FALSE)
```

#Table 1. color dots
```{r}
png("ms/Accessory/output/Table01_dots.png", height=3, width=.2, units="in", res=300)

@@

plot(y~x,dots,cex=1.5,pch=16,xlab="",ylab="",xaxt="n",yaxt="n",col=col.spp(dots$species),bty="n",xlim=c(0.8,1.2),ylim=c(1.8,28.2))
dev.off()
```

@@

write.csv(acc_slopes, file="ms/Accessory/output/Table02_acc_cost_embryo_size_slopes.csv",row.names=FALSE)
```

@@

write.csv(results, file="ms/Accessory/output/Table03_correlations_with_repro_inv.csv",row.names=FALSE)
```

#Figure 01. predictions
```{r}
png("ms/Accessory/output/Figure01b&c_predictions.png", height=3, width=6, units="in", res=300)
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05)) 
plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.2,x1=.9,y0=.9,y1=.2,lty=2)
segments(x0=.1,x1=.8,y0=.8,y1=.1,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="count, scaled to plant size",side=2,line=1.1,outer=FALSE,cex=0.8)
mtext(text="costs (mg/seed)",side=1,line=1.0,outer=FALSE,cex=0.8)
legend("bottomleft",legend=c("seed count by reproductive costs","initiated ovules count by pollen-attraction costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
extra.top.left("b",2,1)

@@

png("ms/Accessory/output/Figure01def_predictions.png", height=6, width=6, units="in", res=300)

@@

#Figure 2
```{r}
png("ms/Accessory/output/Figure02.png", height=9, width=6, units="in", res=300)

@@

#Figure 3. Correlations of various reproductive investment categories against plant weight
```{r}
png("ms/Accessory/output/Figure03_correlations_with_plant_weight.png", height=5, width=10, units="in", res=300)

@@

#Supplementary Table. Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
```{r}
png("ms/Accessory/output/Figure_SXX_RE_RA_size_age_patterns.png", height=10, width=10, units="in", res=300)

@@

write.csv(results, file="ms/Accessory/output/Table05a_accessory_vs_all_repro.csv",row.names=FALSE)

@@

write.csv(results, file="ms/Accessory/output/Table05b_accessory_vs_total_weight.csv",row.names=FALSE)

@@

write.csv(results, file="ms/Accessory/output/Table05c_accessory_vs_age.csv",row.names=FALSE)
dev.off()
```

@@

write.csv(acc_slopes, file="ms/Accessory/output/Table_S1_extra_flower_invest_vs_all_repro_inv.csv",row.names=FALSE)
```

@@

write.csv(results, file="ms/Accessory/output/output/Table07_EXTRA_correlations_with_repro_inv.csv",row.names=FALSE)
```

@@

#Although very little energy goes into propagules (or embryos) a notable amount of energy is required for successful seeds to form
```{r}
png("ms/Accessory/output/FigureXX_success_vs_discarded.png", height=6, width=8, units="in", res=300)

@@

#This effect is true across species, since larger-seeded species produce fewer seeds and have higher per seed accessory costs and true within species, since absolute accessory investment is a function of plant size not seedset
```{r}
png("ms/Accessory/output/FigureXX_EXTRA_acc_cost_by_seed_count.png", height=5, width=5, units="in", res=300)

@@

write.csv(results, file="ms/Accessory/output/TableXX_seedcount_vs_accessory.csv",row.names=FALSE)
